A hazards approach to the biometric analysis of infant mortality

### 2023-03-18 paper2.Rmd
fix glitches

\begin{equation} (\#eq:logcube)
g(t) = C \log^3(t + 1), \; 0 \le t \le 365,
\end{equation}
where $t$ is age measured in days and $C$ is a normalizing constant,
\begin{equation*}
C = \frac{365}{\log^3(366)}.
\end{equation*}

@@

```{r risksets, echo = FALSE, results = 'asis'}
source("R/tbl.R")
lt1 <- with(r1, cbind(ginv(risktimes), round(risktimes, 1), size, n.events))
lt1 <- data.frame(lt1)
names(lt1) <- c("Day", "g(Day)", "Population", "Deaths")
tbl(lt1[1:7, ], caption = "Life table, 1861-1890.")
```

@@

```{r firstlines, results='asis'}
tbl(infant[1:5, 1:6], caption = "First five rows of data frame.")
nro <- nrow(infant)
deat <- as.integer(sum(infant$event))
```

>>>>

\begin{equation} (\#eq:logcube)
g(t) = C \log^3(t + 1), \; 0 \le t \le 365,
\end{equation}
where $t$ is age measured in days and $C$ is a normalizing constant,
\begin{equation*}
C = \frac{365}{\log^3(365 + 1)}.
\end{equation*}

@@

```{r risksets, echo = FALSE, results = 'asis'}
source("R/tbl.R")
lt1 <- with(r1, cbind(ginv(risktimes), round(risktimes, 1), size, n.events))
lt1 <- data.frame(lt1)
names(lt1) <- c("Day", "g(Day)", "Population", "Deaths")
tbl(lt1[c(1:5, 360:364), ], caption = "Life table for infants in Västerbotten, 1861-1890.")
```

@@

```{r firstlines, results='asis'}
out <- infant[1:5, 1:6]
out[3, 2] <- "girl"
out[4, 3] <- 28
tbl(out, caption = "First five rows of data frame.")
nro <- nrow(infant)
deat <- as.integer(sum(infant$event))
```
